``FISTA'' in Banach spaces with adaptive discretisations

### 2021-10-03 paper.tex
Updated Haar example and code

	The proposed generalised FISTA algorithm is stated in Algorithm~\ref{alg: refining FISTA} for an arbitrary choice of \edit{refining subspaces}{closed convex subsets} $\spcf0^n\subset \edit{\spcf0\cap}{}\F H$ for $n=0,1,\ldots$. The only difference \edit{}{from standard FISTA }is that on iteration $n$, all computations are performed in the \edit{subspace}{subset} $\spcf0^n$. If $\spcf0^n\edit{=\spcf0}{}=\F H$ then we recover the \edit{standard FISTA}{original} algorithm.

@@

	\subsection{Computing the convergence bound}
	For Step~\ref{step: step 1 stability} of Section~\ref{sec: recipe} we look to replicate the classical bound of the form in \eqref{eq: classical FISTA} for Algorithm~\ref{alg: refining FISTA}. The proofs in this step follow the classical arguments \cite{Beck2009,Chambolle2015} very closely. 
	\edit{}{Throughout this section we consider a sequence $(\spcf0^n)_{n\in\F N}$ which generate the iterates $(\varf0_n)_{n\in\F N}$ in Algorithm~\ref{alg: refining FISTA} satisfying
	\begin{equation}\label{eq: refining subspace definition}
		\varf0^{n-1}\in\spcf0^n\subset\F H \quad\text{are closed, convex, locally compact subsets for all }\quad n\in\F N.
	\end{equation}}

@@

	Application of Theorem~\ref{thm: generic a_U and a_E} gives $\vars3_{\Varf0}=2^{\frac d2}$ although \edit{although}{} $\Norm\cdot$ is too strong a metric and results in $\vars3_{\op{E}}=2^0$. This can be seen because for any $\varf0\in L^1(\Domain)$ and Dirac mass $\delta$ supported in $(0,1)^d$, 
	\begin{equation}
		\Norm{\varf0-\delta} = \sup_{\vard0\in C(\Domain), \norm{\vard0}_{L^\infty}\leq 1} \IP{\vard0}{\varf0-\delta} = \Norm{\varf0}+\Norm{\delta} \geq 1 = \meshsize^0.
	\end{equation}
	To improve our estimate of $\vars3_{\op{E}}$ requires additional assumptions on $\A$. \edit{}{Note that the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\F H\to\tilde{\spcf0}^k$ onto piecewise-constant functions is $\Norm\cdot$-diminishing. Therefore }
	for any $\varf0\in\F H$, $\varf2\coloneqq \tilde{\tens{\Pi}}_k\varf0\in\tilde{\spcf0}^k$ we have
	\begin{align}
		\op{E}(\varf2)-\op{E}(\varf0) &= \edit{\tfrac12\norm{\A\varf2-\data}_{\ell^2}^2 - \tfrac12\norm{\A\varf0-\data}_{\ell^2}^2}{\op{f}(\A\varf2-\data)-\op{f}(\A\varf0-\data)} + \mu\left(\Norm{\varf2}-\Norm{\varf0}\right)
		\\&\leq \ip{\nabla \op{f}(\A\varf2-\data)}{\A(\varf2-\varf0)}
		\\&\leq\edit{\max(\norm{\A\varf2-\data}_{\ell^2},\norm{\A\varf0-\data}_{\ell^2})}{\left[\norm{\nabla\op{f}(\A\varf0^*-\data)}_{\ell^2} + \norm{\A(\varf2-\varf0^*)}_{\ell^2}\right]}\norm{\A(\varf2-\varf0)}_{\ell^2}.
	\end{align}
	\edit{Choosing $\varf2 = \tilde{\tens{\Pi}}_k\varf0^*$ for any bounded linear extension to the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\spcf0\to\tilde{\spcf0}^k$ gives
	\\\centerline{$\displaystyle\op{E}(\varf2)-\op{E}(\varf0^*) \lesssim \norm{\A(\tilde{\tens{\Pi}}_k\varf0^*-\varf0^*)}_{\ell^2} \leq \norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty}\Norm{\varf0^*}.$}
	Expanding the operator norm further,
	\\\centerline{$\displaystyle
		\norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty} = \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain} \frac{|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|}{\norm{\vvarx3}_{\ell^2}} \leq \sup_{\vvarx3\in\R^m} \frac{\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}}{\norm{\vvarx3}_{\ell^2}} 
		= \sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1}$}
	}{Clearly $\norm{\nabla\op{f}(\A\varf0^*-\data)}_{\ell^2}$ is a constant, the second term is bounded by
	\begin{equation}
	\norm{\A(\varf2-\varf0^*)}_{\ell^2} = \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} \IP{\A^*\vvarx3}{\varf2-\varf0^*} \leq \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} |\A^*\vvarx3|_{L^\infty}\Norm{\varf2-\varf0^*} \leq |\A^*|_{\ell^2\to C^0}(\Norm{\varf0}+\Norm{\varf0^*}).
	\end{equation}
	Similarly, the final term can be approximated by
	\begin{multline}
		\norm{\A(\tilde{\tens{\Pi}}_k\varf0-\varf0)}_{\ell^2}
		 = \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} \IP{(\tilde{\tens{\Pi}}_k-\id)\A^*\vvarx3}{\varf0}
		\leq \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain}|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|\:\norm{\vvarx3}_{\ell^2}^{-1}\Norm{\varf0}
		\\\leq \sup_{\vvarx3\in\R^m}\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}\: \norm{\vvarx3}_{\ell^2}^{-1} \Norm{\varf0}\quad=\sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1} \Norm{\varf0}
	\end{multline}}
	where $\sqrt d2^{-k}$ is the diameter of a $d$ dimensional pixel of side length $2^{-k}$. \edit{}{Sub-levelsets of $\op{E}$ are compact in $L^1(\Domain)$, therefore there exists a weak$^*$-converging minimising sequence $\varf0^*_j\in\F H$ such that $\varf0^*_j\rightharpoonup\varf0^*$ and $\lim_{j\to\infty}\op{E}(\varf0^*_j)=\op{E}(\varf0^*)$. 
		Combining these estimates gives 
		\begin{equation}
			\inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0^*) = \lim_{j\to\infty} \inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0_j^*) \leq \lim_{j\to\infty} \op{E}(\tilde{\tens{\Pi}}_k\varf0_j^*)-\op{E}(\varf0_j^*) \lesssim 2^{-k}.
		\end{equation}}

@@

	\subsection{2D \edit{wavelet Lasso}{robust sparse wavelet reconstruction}}\label{sec: wavelet examples}
	In this example we consider $\A$ to be a 2D Radon transform. In particular, the rows of $\A$ correspond to integrals over the sets $\F{X}^I_i$ where 
	\begin{equation}
		\F{X}_i^I = \left\{\vvarx0\in[-\tfrac12,\tfrac12]^2\st \ip{\vvarx0}{\begin{pmatrix}\cos\theta_I\\\sin\theta_I\end{pmatrix}}\in \left[-\tfrac12+\tfrac{i-1}{50},-\tfrac12+\tfrac{i}{50}\right)\right\}, \quad \theta_I=\frac{180^\circ}{51}I \quad \text{ for } i,I=1,2,\ldots,50.
	\end{equation}
	This is not exactly in the form analysed by Theorem~\ref{thm: norm bound examples}, however only the sets $\{\F{X}^I_i\st i\in[50]\}$ for each $I$ are disjoint, therefore we apply Theorem~\ref{thm: norm bound examples} block-wise to estimate
	\begin{equation}
		\norm{\A}_{L^2\to\ell^2} \leq \sqrt{\sum_{I\in[50]}\max_{i\in[50]} |\F{X}^I_i|} = \sqrt{\sum_{I\in[50]}\max_{i\in[50]} \int_{\F{X}^I_i}1d\vvarx0}= \sqrt{\sum_{I\in[50]}\max_{i\in[50]}\ (\A\1)_{i,I}}\;.
	\end{equation}
	$\A$ is not smooth, therefore we can't bound $|\A^*|_{C^k}$ for $k>0$, and so we must look to minimise over $\ell^1$ rather than $L^1$. The natural choice is to promote sparsity in a wavelet basis which can be rearranged into the \edit{Lasso}{} form \edit{}{of \eqref{eq: Lasso energy}}:
	\begin{equation}
		\min_{\varf0\in \spcf0} \edit{\tfrac12\norm{\A\varf0-\data}_{\ell^2}^2}{\op{f}(\A\varf0-\data)} + \mu \norm{\tens{W}^{-1}\varf0}_{\ell^1} = \min_{\hat{\varf0}\in\ell^1(\R)} \edit{\tfrac12\norm{\A\tens{W}\hat{\varf0}-\data}_{\ell^2}^2}{\op{f}(\A\tens{W}\hat{\varf0}-\data)} + \mu \norm{\hat{\varf0}}_{\ell^1}.
	\end{equation}
	The minimisers are related by $\varf0^* = \tens{W}\hat{\varf0}^*$ and, for wavelet bases, $\tens{W}$ is orthonormal so $\norm{\A\tens{W}}_{\ell^2\to\ell^2} = \norm{\A}_{L^2\to\ell^2}$. 
	\edit{}{ In this example we consider the smoothed robust fidelity \cite{Rosset2007}
		\begin{equation}
			\op{f}(\vvard0) = \sum_{i=1}^m \splitln{10^{-4}|\vard0_i|}{|\vard0_i|\geq10^{-4}}{\tfrac12|\vard0_i|^2+\tfrac12 10^{-8}}{\text{else}} \approx 10^{-4}\norm{\vvard0}_{\ell^1}.
		\end{equation}
	}	
	From Section~\ref{sec: Lasso gap and gradient} we know that to track convergence and perform adaptive refinement, it is sufficient to accurately bound $|[\tens{W}^\top \A^*\vvard0_n]_j|$ for all $j\notin J_n$. If $\tens{W}$ is a wavelet transformation then its columns, $w_j\in L^2$, are simply the wavelets themselves and we can use the bound 
	\begin{equation}
		|\IP{w_j}{\A^*\vvard0_n}| = \left|\IP{w_j}{\1_{\supp(w_j)}\A^*\vvard0_n}\right| \leq \norm{\1_{\supp(w_j)} \A^*\vvard0_n}_{L^2}\leq \norm{\1_{\F{X}} \A^*\vvard0_n}_{L^2}
	\end{equation}
	for all $\F{X}\supset \supp(w_j)$.
	In the case of the Radon transform, we can compute the left-hand side explicitly for the finitely many $j\in J_n$ but we wish to use the right-hand side in a structured way to avoid computing the infinitely many $j\notin J_n$. To do this, we will take a geometrical perspective on the construction of wavelets to view them in a tree format.

@@

	\paragraph{Numerical results}
	We consider two phantoms where the ground-truth is either a binary disc or the Shepp-Logan phantom. No noise is added to the Shepp-Logan data but \SI{5}{\percent} \edit{Gaussian white}{Laplace distributed} noise is added to the disc data. This is visualised in Figure~\ref{fig: haar data}. All optimisations shown will be spatially adaptive using Haar wavelets and initialised with $\spcf0^0= \{\varx0\mapsto c\st c\in\F R\}$. The gradient metric shown throughout is the $\ell^2$ norm. Motivated by \eqref{eq: wavelet error metric}, the spatial adaptivity is chosen to refine nodes $j\in\op{leaf}(J_n)$ to ensure that 
	$$ \norm{\1_{\supp(w_j)}\A^*\vvard0_n}_{L^2} -\mu  \leq 10\Norm{\partial_n\op{E}(\varf0_n)}_*$$
	for all $j$ and $n$ (i.e. so that the continuous gradient is less than 10 times the discrete gradient).

	The first numerical results shown in Figure~\ref{fig: haar convergence} compare the same adaptive algorithms as shown in Figure~\ref{fig: convergence with method}. In these examples we see that the greedy FISTA and the $a=20$ algorithms achieve almost linear convergence while $a=2$ is significantly slower.

	\begin{figure}\centering
		\includegraphics[width=.85\textwidth]{haar_data}
		\caption{Phantoms\edit{ and}{,} data \edit{used }{and reconstructions }for wavelet-sparse tomography optimisation. The Shepp-Logan data is exact but the data for the disc-phantom has \SI{5}{\percent}\ \edit{Gaussian white}{Laplace distributed} noise. Without noise the data would be uniform with respect to the angle.}\label{fig: haar data}

>>>>

	The proposed generalised FISTA algorithm is stated in Algorithm~\ref{alg: refining FISTA} for an arbitrary choice of \edit{refining subspaces}{closed convex subsets} $\spcf0^n\subset \edit{\spcf0\cap}{}\F H$ for $n\in\F N$. The only difference \edit{}{from standard FISTA }is that on iteration $n$, all computations are performed in the \edit{subspace}{subset} $\spcf0^n$. If $\spcf0^n\edit{=\spcf0}{}=\F H$, then we recover the \edit{standard FISTA}{original} algorithm. \edit{}{More generally, the idea is that $\spcf0^n$ are `growing', for example $\spcf0^n\subset\spcf0^{n+1}$, but this assumption is not necessary in most of the results.}

@@

	\subsection{Computing the convergence bound}
	For Step~\ref{step: step 1 stability} of Section~\ref{sec: recipe} we look to replicate the classical bound of the form in \eqref{eq: classical FISTA} for Algorithm~\ref{alg: refining FISTA}. The proofs in this step follow the classical arguments \cite{Beck2009,Chambolle2015} very closely. 
	\edit{}{Throughout this section we consider a sequence $(\spcf0^n)_{n\in\F N}$ which generate the iterates $(\varf0_n)_{n\in\F N}$ in Algorithm~\ref{alg: refining FISTA} such that
	\begin{equation}\label{eq: refining subspace definition}
		\varf0^{n-1}\in\spcf0^n\subset\F H \quad\text{where }\spcf0^n\text{ is a closed, convex, locally compact subset for all } n\in\F N.
	\end{equation}}

@@

	Application of Theorem~\ref{thm: generic a_U and a_E} gives $\vars3_{\Varf0}=2^{\frac d2}$ although \edit{although}{} $\Norm\cdot$ is too strong a metric and results in $\vars3_{\op{E}}=2^0$. This can be seen because for any $\varf0\in L^1(\Domain)$ and Dirac mass $\delta$ supported in $(0,1)^d$, 
	\begin{equation}
		\Norm{\varf0-\delta} = \sup_{\vard0\in C(\Domain), \norm{\vard0}_{L^\infty}\leq 1} \IP{\vard0}{\varf0-\delta} = \Norm{\varf0}+\Norm{\delta} \geq 1 = \meshsize^0.
	\end{equation}
	To improve our estimate of $\vars3_{\op{E}}$ requires additional assumptions on $\A$. \edit{}{Note that the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\F H\to\tilde{\spcf0}^k$ onto piecewise-constant functions is $\Norm\cdot$-diminishing. Therefore }
	for any $\varf0\in\F H$, $\varf2\coloneqq \tilde{\tens{\Pi}}_k\varf0\in\tilde{\spcf0}^k$ we have
	\begin{align}
		\op{E}(\varf2)-\op{E}(\varf0) &= \edit{\tfrac12\norm{\A\varf2-\data}_{\ell^2}^2 - \tfrac12\norm{\A\varf0-\data}_{\ell^2}^2}{\op{f}(\A\varf2-\data)-\op{f}(\A\varf0-\data)} + \mu\left(\Norm{\varf2}-\Norm{\varf0}\right)
		\\&\leq \ip{\nabla \op{f}(\A\varf2-\data)}{\A(\varf2-\varf0)}
		\\&\leq\edit{\max(\norm{\A\varf2-\data}_{\ell^2},\norm{\A\varf0-\data}_{\ell^2})}{\left[\norm{\nabla\op{f}(\A\varf0^*-\data)}_{\ell^2} + \norm{\A(\varf2-\varf0^*)}_{\ell^2}\right]}\norm{\A(\varf2-\varf0)}_{\ell^2}.
	\end{align}
	\edit{Choosing $\varf2 = \tilde{\tens{\Pi}}_k\varf0^*$ for any bounded linear extension to the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\spcf0\to\tilde{\spcf0}^k$ gives
	\\\centerline{$\displaystyle\op{E}(\varf2)-\op{E}(\varf0^*) \lesssim \norm{\A(\tilde{\tens{\Pi}}_k\varf0^*-\varf0^*)}_{\ell^2} \leq \norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty}\Norm{\varf0^*}.$}
	Expanding the operator norm further,
	\\\centerline{$\displaystyle
		\norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty} = \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain} \frac{|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|}{\norm{\vvarx3}_{\ell^2}} \leq \sup_{\vvarx3\in\R^m} \frac{\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}}{\norm{\vvarx3}_{\ell^2}} 
		= \sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1}$}
	}{Clearly $\norm{\nabla\op{f}(\A\varf0^*-\data)}_{\ell^2}$ is a constant. For the second term, recall $\Norm{\varf2}\leq \Norm{\varf0}$, therefore we can bound
	\begin{equation}
	\norm{\A(\varf2-\varf0^*)}_{\ell^2} = \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} \IP{\A^*\vvarx3}{\varf2-\varf0^*} \leq \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} |\A^*\vvarx3|_{L^\infty}\Norm{\varf2-\varf0^*} \leq |\A^*|_{\ell^2\to C^0}(\Norm{\varf0}+\Norm{\varf0^*}).
	\end{equation}
	Similarly, the final term can be approximated by
	\begin{multline}
		\norm{\A(\tilde{\tens{\Pi}}_k\varf0-\varf0)}_{\ell^2}
		 = \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} \IP{(\tilde{\tens{\Pi}}_k-\id)\A^*\vvarx3}{\varf0}
		\leq \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain}|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|\:\norm{\vvarx3}_{\ell^2}^{-1}\Norm{\varf0}
		\\\leq \sup_{\vvarx3\in\R^m}\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}\: \norm{\vvarx3}_{\ell^2}^{-1} \Norm{\varf0}\quad=\sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1} \Norm{\varf0}
	\end{multline}}
	where $\sqrt d2^{-k}$ is the diameter of a $d$ dimensional pixel of side length $2^{-k}$. \edit{}{Sub-levelsets of $\op{E}$ are compact in $L^1(\Domain)$, therefore there exists a weak$^*$-converging minimising sequence $\varf0^*_j\in\F H$ such that $\varf0^*_j\rightharpoonup\varf0^*$ and $\lim_{j\to\infty}\op{E}(\varf0^*_j)=\op{E}(\varf0^*)$. 
		Combining these estimates gives 
		\begin{equation}
			\inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0^*) = \lim_{j\to\infty} \inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0_j^*) \leq \lim_{j\to\infty} \op{E}(\tilde{\tens{\Pi}}_k\varf0_j^*)-\op{E}(\varf0_j^*) \lesssim 2^{-k}.
		\end{equation}}

@@

	\subsection{2D \edit{wavelet Lasso}{robust sparse wavelet reconstruction}}\label{sec: wavelet examples}
	In this example we consider $\A$ to be a 2D Radon transform. In particular, the rows of $\A$ correspond to integrals over the sets $\F{X}^I_i$ where 
	\begin{equation}
		\F{X}_i^I = \left\{\vvarx0\in[-\tfrac12,\tfrac12]^2\st \ip{\vvarx0}{\begin{pmatrix}\cos\theta_I\\\sin\theta_I\end{pmatrix}}\in \left[-\tfrac12+\tfrac{i-1}{100},-\tfrac12+\tfrac{i}{100}\right)\right\}, \quad \theta_I=\frac{180^\circ}{51}I
	\end{equation}
	for $i=1,\ldots,50$, $I=1,\ldots,100$.
	This is not exactly in the form analysed by Theorem~\ref{thm: norm bound examples}, however only the sets $\{\F{X}^I_i\st i\in[100]\}$ for each $I$ are disjoint, therefore we apply Theorem~\ref{thm: norm bound examples} block-wise to estimate
	\begin{equation}
		\norm{\A}_{L^2\to\ell^2} \leq \sqrt{\sum_{I\in[50]}\max_{i\in[100]} |\F{X}^I_i|} = \sqrt{\sum_{I\in[50]}\max_{i\in[100]} \int_{\F{X}^I_i}1d\vvarx0}= \sqrt{\sum_{I\in[50]}\max_{i\in[100]}\ (\A\1)_{i,I}}\;.
	\end{equation}
	$\A$ is not smooth, therefore we can't bound $|\A^*|_{C^k}$ for $k>0$, and so we must look to minimise over $\ell^1$ rather than $L^1$. The natural choice is to promote sparsity in a wavelet basis which can be rearranged into the \edit{Lasso}{} form \edit{}{of \eqref{eq: Lasso energy}}:
	\begin{equation}
		\min_{\varf0\in \spcf0} \edit{\tfrac12\norm{\A\varf0-\data}_{\ell^2}^2}{\op{f}(\A\varf0-\data)} + \mu \norm{\tens{W}^{-1}\varf0}_{\ell^1} = \min_{\hat{\varf0}\in\ell^1(\R)} \edit{\tfrac12\norm{\A\tens{W}\hat{\varf0}-\data}_{\ell^2}^2}{\op{f}(\A\tens{W}\hat{\varf0}-\data)} + \mu \norm{\hat{\varf0}}_{\ell^1}.
	\end{equation}
	The minimisers are related by $\varf0^* = \tens{W}\hat{\varf0}^*$ and, for wavelet bases, $\tens{W}$ is orthonormal so $\norm{\A\tens{W}}_{\ell^2\to\ell^2} = \norm{\A}_{L^2\to\ell^2}$. 
	\edit{}{ In this example we consider the smoothed robust fidelity \cite{Rosset2007}
		\begin{equation}
			\op{f}(\vvard0) = \sum_{i=1}^m \splitln{10^{-4}|\vard0_i|}{|\vard0_i|\geq10^{-4}}{\tfrac12|\vard0_i|^2+\tfrac12 10^{-8}}{\text{else}} \approx 10^{-4}\norm{\vvard0}_{\ell^1}.
		\end{equation}
	}	
	From Section~\ref{sec: Lasso gap and gradient} we know that to track convergence and perform adaptive refinement, it is sufficient to accurately bound $|[\tens{W}^\top \A^*\vvard0_n]_j|$ for all $j\notin J_n$. If $\tens{W}$ is a wavelet transformation then its columns, $w_j\in L^2$, are simply the wavelets themselves and we can use the bound 
	\begin{equation}
		|\IP{w_j}{\A^*\vvard0_n}| = \left|\IP{w_j}{\1_{\supp(w_j)}\A^*\vvard0_n}\right| \leq \norm{\1_{\supp(w_j)} \A^*\vvard0_n}_{L^2}\leq \norm{\1_{\F{X}} \A^*\vvard0_n}_{L^2}
	\end{equation}
	for all $\F{X}\supset \supp(w_j)$.
	In the case of the Radon transform, we can compute the left-hand side explicitly for the finitely many $j\in J_n$ but we wish to use the right-hand side in a structured way to avoid computing the infinitely many $j\notin J_n$. To do this, we will take a geometrical perspective on the construction of wavelets to view them in a tree format.

@@

	\paragraph{Numerical results}
	We consider two phantoms where the ground-truth is either a binary disc or the Shepp-Logan phantom. \edit{No noise is added to the Shepp-Logan data but 5\% Gaussian white noise is added to the disc data.}{Both examples are corrupted with \SI{2}{\percent} Laplace distributed noise.} This is visualised in Figure~\ref{fig: haar data}. All optimisations shown are spatially adaptive using Haar wavelets and initialised with $\spcf0^0= \{\varx0\mapsto c\st c\in\F R\}$. The gradient metric shown throughout is the $\ell^2$ norm. Motivated by \eqref{eq: wavelet error metric}, the spatial adaptivity is chosen to refine nodes $j\in\op{leaf}(J_n)$ to ensure that 
	$$ \norm{\1_{\supp(w_j)}\A^*\vvard0_n}_{L^2} -\mu  \leq 10\Norm{\partial_n\op{E}(\varf0_n)}_*$$
	for all $j$ and $n$ (i.e. so that the continuous gradient is less than 10 times the discrete gradient).

	The first numerical results shown in Figure~\ref{fig: haar convergence} compare the same adaptive algorithms as shown in Figure~\ref{fig: convergence with method}. In these examples we see that the greedy FISTA and the $a=20$ algorithms achieve almost linear convergence while $a=2$ is significantly slower. \edit{}{Interestingly, in both examples the $a=20$ variant uses half as many wavelets as the Greedy variant, and therefore converges slightly faster in time. }

	\begin{figure}\centering
		\includegraphics[width=.85\textwidth]{haar_data}
		\caption{Phantoms\edit{ and}{,} data \edit{used }{and reconstructions }for wavelet-sparse tomography optimisation. \edit{The Shepp-Logan data is exact but the data for the disc-phantom has}{Both examples are corrupted with} \SI{2}{\percent}\ \edit{Gaussian white}{Laplace distributed} noise. }\label{fig: haar data}
